---
title: "CovidSurg"
output:
  flexdashboard::flex_dashboard:
    theme: cosmo
    #orientation: row
    #source_code: embed
runtime: shiny
---

<style>
.colored {
  background-color: #F1D64D;
}
</style>

```{r global, include=FALSE}

#ManuscriptFebFinalDataLonger_20220203_0327
set.seed(132)
old <- Sys.time() # get start time

library(flexdashboard)
library(tidyverse)
library(ggsci)
library(knitr)
library(DT)
library(reshape)
library(dummies)
library(ggpubr)
#library(flextable)
#library(officer)
#library(webshot)
#library(magick)


```




```{r}


vars <- readRDS("Vars.rds")
m2 <- readRDS("Calculator2.rds") 
m <- readRDS("CalculatorHotEncoding.rds")
CountPerVal <- readRDS("CountPerValDerivation.rds")

m[m$term== "Intercept",]$Other <- 0

 
EqsFun <- function(xx,data , m){

xx <- xx %>%
  select((order(colnames(.))))

xx2 <- xx %>%
  pivot_longer(everything()) %>%
  unite("All", name:value, sep="_") 

m2 <- filter(m, term %in% c("Intercept", xx2$All))

linpred <- sum(m2$Other)

h <- data %>%
  add_column(
    G1 = linpred
  ) 
  
  return(h)
}

#Tablize <- function(pp) {
#  
#  
#  ft <- flextable(pp)
#  ft <- colformat_num(x = ft, 
#                      big.mark=",", digits = 3, na_str = #"N/A")
#  ft <- autofit(ft) %>%
#    theme_zebra( odd_header = "transparent",
#                 odd_body = "#0073C299",
#                 even_header = "blue",
#                 even_body = "#EFC00099") %>%
#    align(align = "center", part = "all") %>%
#    flextable::border(border.top = fp_border(color = "black"), #border.bottom = fp_border(color = "black"), part = "all" )
#  
#  ft
#}


```

# Disclaimer { data-orientation=columns}

### <b><font size="10em" color="#000000">__Welcome to the CovidSurg Pulmonary Risk calculator__</font></b>  

<b><font size="5em"> __Warning__ </font></b>  

<font size="5"> PLEASE NOTE: This risk calculator tool is __NOT__ intended for use to support or direct clinical decision-making. It is __ONLY__ to be used for academic research, peer review and validation purposes. This tool must __NOT__ be used with data or information relating to any individual patient or individual undergoing active medical treatment.</font>

<b><font size="5"> For full terms and conditions, please contact legalservices@contacts.bham.ac.uk at the University of Birmingham.</font></b>

<font size="5"> This is an academic research calculator and the University of Birmingham accept no responsibility for clinical use or misuse of this tool </font>

 

# Model { data-orientation=columns  data-icon="fa-project-diagram"}

Row {.sidebar  data-width=650}
-----------------------------------------------------------------------
```{r}
#library(tibble)
xx <- tribble(~Age,  ~Sex, ~ASA_grade, ~Preexisting_respiratory_disease,~BUPA_operation_grade,~Anaesthetic_type,~RCRI,~Country_income_SARSCoV2_risk, ~Indication, ~Compartment,
                     "60-69 years", "Female","Grade 1","Yes", "Major","General", "2",  "Upper middle income_Low", "Cancer", "Thoracic")
```


```{r}

h3("Patient characteristics ")

#style = "background-color: #EFF811",

fillCol(height = 390, width= 600, flex = c(NA, 1), 
          inputPanel(
            selectInput(names(vars)[[1]], "Age ", choices = vars[[1]]), 
            selectInput(names(vars)[[2]], "Sex ", choices = vars[[2]]), 
            selectInput(names(vars)[[3]], "ASA grade: ", choices = vars[[3]]), 
            selectInput(names(vars)[[6]], "BUPA_operation_grade", choices = vars[[6]]),
            selectInput(names(vars)[[5]], "Preexisting respiratory disease", choices = vars[[5]]),
            selectInput(names(vars)[[4]], "RCRI", choices = vars[[4]]),
            selectInput(names(vars)[[8]], "Anaesthetic type", choices = vars[[8]]),
            selectInput(names(vars)[[13]], "Indication", choices = vars[[13]]),
            selectInput(names(vars)[[15]], "Country_income_SARSCoV2_risk", choices = vars[[15]]),
            selectInput(names(vars)[[12]], "Compartment", choices = vars[[12]])
          ), style = "background-color: light blue;", align = "center"
)


#h3("Selected variables ")

 newdat  <- reactive({
    tribble(~Age,  ~Sex, ~ASA_grade, ~Preexisting_respiratory_disease,~BUPA_operation_grade,~Anaesthetic_type,~RCRI,~Country_income_SARSCoV2_risk, ~Indication, ~Compartment,
                     input$Age, input$Sex,input$ASA_grade,input$Preexisting_respiratory_disease, input$BUPA_operation_grade,input$Anaesthetic_type, input$RCRI,  input$Country_income_SARSCoV2_risk,input$Indication, input$Compartment)
  })
 
 h3("")
 h3("")
```

### Calculator table

```{r}
#renderDT({
#  DT::datatable(newdat(),rownames= FALSE)
#  
#})

pp <- m %>%
  filter(Other != 0) %>%
  select(term, Other) %>%
  mutate(Other = paste0("+ ",Other ))

names(pp) <- c("Variables", "Score")


#renderPlot({ 
#  
#  l2 <- Tablize(pp)
#  
#  print(plot( l2))
#  
#},bg="transparent")

tags$iframe(style="height:550px; width:100%; scrolling=yes",
src="Table.pdf")  #put better

```

```{r}
h3("About us")


```

__Model Development Team__ (alphabetical by surname):

* Laura Bravo
* Victor Roth Cardoso
* James Glasbey
* Georgios Gkoutos
* Elizabeth Li
* Dmitri Nepogodiev
* Omar Omar
* Joana Simoes
* Luke Slater
* Aneel Bhangu (guarantor)

A full list of COVIDSurg collaborators will be presented in the final published paper.

### Row 
-----------------------------------------------------------------------

```{r }
 
Fin  <- reactive({
    
    Fin <- EqsFun(newdat(), newdat(), m)
     Fin

  })




``` 


### Score sum

```{r}


Result <- reactive({
  
  if ( Fin()$G1 > 3 & Fin()$G1 <19) {
  
  
  Result <- CountPerVal %>%
    filter( linpred2 == as.numeric(Fin()$G1)) %>%
    select(Div)
  
  out <- Result$Div
  
  }else {
    
    
    out <- " "
  }
  
out
  
})

renderValueBox({
  valueBox(
    value = paste0("Pulmonary complication risk: ",Result(), " %"),
    caption = paste0("Calculator number: ", as.numeric(Fin()$G1)),
    icon = "fa-calculator"
    )
})
```


```{r}
h3("")
```


### Validation data 

```{r}
renderPlot({
    

p1 <- ggbarplot(CountPerVal, x = "linpred2", y = "n",
                fill = "#0073C299",               # change fill color by cyl
                color = "white",            # Set bar border colors to white
                palette = "jco",            # jco journal color palett. see ?ggpar
                #sort.val = "asc",           # Sort the value in ascending order
                sort.by.groups = TRUE, 
                x.text.angle = 90           # Rotate vertically x axis texts
) + geom_vline(xintercept = as.character(Fin()$G1), linetype="dotted", 
               color = "#86868699", size=1) + ylab("Number of patients") + xlab(" ")

p2 <- ggbarplot(CountPerVal, x = "linpred2", y = "Div",
                fill = "#EFC00099",               # change fill color by cyl
                color = "white",            # Set bar border colors to white
                palette = "jco",            # jco journal color palett. see ?ggpar
                #sort.val = "asc",
                label = TRUE, label.pos = "out",# Sort the value in ascending order
                lab.col = "#86868699",
                lab.size = 4,
                lab.nb.digits = 1,# Sort inside each group
                sort.by.groups = TRUE,      # Sort inside each group
                x.text.angle = 90           # Rotate vertically x axis texts
) + geom_vline(xintercept = as.character(Fin()$G1), linetype="dotted", 
               color = "#86868699", size=1) + xlab("Predicted score") + ylab("Pulmonary complication (%)") 

figure <- ggarrange(p1, p2 ,
                    ncol = 1, nrow = 2)



print(
  
  figure
  #annotate_figure(figure,
   #             fig.lab = "Validation dataset results", fig.lab.face = "bold")

)


 })
  
# width = 800, height =580,
```
